Machine Learning for Handwriting Recognition: Algorithms and Techniques

### 2023-11-18 Manuscript/Manuscript.tex
General Commits - Fixing Grammar Issue

\section* {Abstract}
Will be Implemented after the article is finished.

\section* {Keywords}
Machine Learning, Deep Learning, Handwriting Recognition, Activation Function, Model, Parameters...

@@

\section* {Fundemental Concepts}
In the realm of machine learning, a foundational understanding is crucial for advancing applications such as handwriting recognition. And Since handwriting is process of training in machine learning, or more accurately, in deep learning, We need to figure out, the difference between each algorithm, including CNN, RNN and LSTNs, also, we have to deeply distinguish the supervised and unsupervised learning in machine learning field distinctively.

\paragraph{Basics of Machine Learning}
So what is machine learning? Essentially, machine learning is a subset of artificial intelligence that allows systems to learn and improve from experience without being explicitly programmed. This learning process is driven by algorithms that interpret and process data, extract patterns and make decisions. In handwriting recognition, these algorithms play a crucial role in decoding the diversity and complexity of human handwriting. Machine learning can be divided into three main types: supervised learning, where models are trained on labeled data; unsupervised learning, which processes unlabeled data and aims to discover hidden patterns; and reinforcement learning, where models learn through trial and error. Decision-making techniques. Each learning type has a unique impact on handwriting recognition.

\paragraph{Handwriting Recognition Specifics}
Similarly, handwriting is also a process of the training in the field of machine learning. As a specialized application of machine learning, it entails the intricate process of converting handwritten text into a digital format that machines can interpret. This task presents unique challenges, primarily due to the vast variability and individuality inherent in human handwriting. Unlike typed text, handwritten characters and words can vary greatly in size, style, alignment, and stroke thickness, even within a single document. Additionally, cursive handwriting introduces complexities such as connected letters and overlapping strokes, making the task of segmentation and recognition notably challenging. In the context of machine learning, these challenges necessitate sophisticated algorithms capable of handling such variability and ambiguity.

@@

As you can see

@@

This paragraph just put an ReLu function outside of the layers and that is the activation function of the layer to ensure to produce the real probability.

@@

\bibliographystyle{plain}
\bibliography{Citations.bib}
\cite{824821}
\cite{NIPS2008_66368270}
\cite{6981034}
\end{document}

>>>>

\section* {Abstract}
As topic said, this paper mainly focused on machine learning and handwriting recognition, an area that has grown significantly due to the development of powerful algorithms and sophisticated techniques. It explores the role of machine learning from the basic concepts, data collection methods, data augmentation techniques, and various algorithmic approaches to handwriting recognition, including traditional machine learning and neural networks, a newer way. This article also discusses the impact of machine learning on the connection between human interactions and digital systems, highlighting its potential to improve user experience and facilitate digital interactions. By examining methods and advances in the field, the article reveals the future possibilities and applications of machine learning for accurately and efficiently processing handwritten text.

%\section* {Keywords}
%Machine Learning, Deep Learning, Handwriting Recognition, Activation Function, Model, Parameters...

@@

\section* {Fundemental Concepts}
So what is machine learning? Essentially, machine learning is a subset of artificial intelligence that allows the systems and software to learn and improve from the dataset or experience without being explicitly programmed. This learning process is driven by algorithms that interpret and process data, extract patterns and make decisions. In handwriting recognition, the algorithms play a vital role in decoding the diversity and complexity of human handwriting. Machine learning can be divided into three main types: supervised learning, where models are trained on labeled data; unsupervised learning, which processes unlabeled data and aims to discover hidden patterns; and reinforcement learning, where models learn through trial and error.Each learning type has a unique impact on handwriting recognition.

In the realm of machine learning, a foundational understanding is crucial for advancing applications such as handwriting recognition. And Since handwriting is process of training in machine learning, or more accurately, in deep learning, We need to figure out, the difference between each algorithm, including CNN, RNN and LSTNs, also, we have to deeply distinguish the supervised and unsupervised learning in machine learning field distinctively.

\paragraph{Handwriting Recognition Specifics}
The handwriting is also a process of the training in the field of machine learning. As a specialized application of machine learning, it entails the intricate process of converting handwritten text into a digital format that machines can interpret. This task presents unique challenges, primarily due to the vast variability and individuality inherent in human handwriting. Unlike typed text, handwritten characters and words can vary greatly in size, style, alignment, and stroke thickness, even within a single document. Additionally, cursive handwriting introduces complexities such as connected letters and overlapping strokes, making the task of segmentation and recognition notably challenging. In the context of machine learning, these challenges necessitate sophisticated algorithms capable of handling such variability and ambiguity.

@@

As you can see, if we first use exponential function, add them together to obtain a sum, then we use this sum as the denominator, we can get a value between 0 and 1. And this number is what we want. However, if you want these values contain the meaning of probability, or, in other words, "become the probability", you may need to add the activation function. In the example below, the code will show how the activation function works.

@@

This paragraph just put an ReLu function outside of the layers and that is the activation function of the layer to ensure to produce the real probability. We have a variaty of activation functions to choose, including

@@

\section*{Discussion}
If you merge the code above with this line of code below, 
\bibliographystyle{plain}
\bibliography{Citations.bib}
\cite{824821}
\cite{NIPS2008_66368270}
\cite{6981034}
\end{document}
